 \documentclass[ notitlepage, prl]{ revtex4-1}
%\documentclass[ notitlepage]{ article}
\setlength{\parindent}{0}
\begin{document}
\author{Kyle Thomas}
\title{R\'esum\'e}
\date{\today}
\maketitle
\section*{Objective}
Having spent years calculating expected results for school, I yearn for the reward of disigning something new and innovative.
That said, I revel in analysis, optimization, and learning new tools. The excitement I get from these topics, along with the critical thought assured by my education in physics, make me a productive asset in all technical endeavors.

section*{Education}
par I received my bachelors of physics from Oregon State University (\textbf {OSU}) in 2015.
par I received my associates with an emphasis in engineering from Southwestern Oregon Community College (\textbf {SWOCC}) in 2011.

section*{Work Experience}
begin{itemize}
\item I proctored exams for various introductory physics courses at OSU during 2014 and 2015.
Proctoring was mainly clarifying exam questions at a student's request.
\item I did unpaid research in Professor Bo Sun's cell biophysics lab at OSU during 2013 and 2014.
With data yielded by this research, I produced my undergraduate thesis, using Matlab code I wrote to segment cells and measure their morphology.
\item I tutored math at OSU and SWOCC from 2009 to 2014.
end{itemize}

section*{Qualifications}
My qualifications include:
begin{itemize}
item six months' experience with the tools and protocols of a cell biophysics lab;
item an education in POSIX operating systems, AutoCAD, and engineering cost-analysis;
item a CompTIA A+ PC technician's certification;
item a passion for innovation and prototyping;
item a familiarity with \LaTeX, python, C++, xhtml, css, and git; and
item a fascination with learning new concepts, software, programming languages, protocols, standards, and best-practices.
end{itemize}
end{document}
