 \documentclass[ notitlepage, prl]{ revtex4-1}
%\documentclass[ notitlepage]{ article}
\setlength{\parindent}{0}
\begin{document}
\author{Kyle Thomas}
\title{R\'esum\'e}
\date{\today}
\maketitle
\section*{Objective}
I wish to advance computer vision algorithms using the education I have achieved along with my physics degree. I have several ideas of how to do this which I'm happy to discuss in interview.

I have hatched ideas to advance object tracking and object recognition through image analysis that I hope to work with. I am excited to learn and advance industrial prototyping practices. I desire to work hard producing deliverables in any of many exciting fields.
\section*{Education}
\par I received my bachelors of physics from Oregon State University (\textbf {OSU}) in 2015.
\par I received my associates with an emphasis on engineering from Southwestern Oregon Community College (\textbf {SWOCC}) in 2011.
\section*{Work Experience}
\begin{itemize}
\item I proctored exams for various introductory physics courses at OSU during 2014 and 2015. Proctoring entailed clarifying exam questions at the students' request.
\item I did unpaid research in Professor Bo Sun's cell biophysics lab at OSU during 2013 and 2014. With data yielded by this research, I produced my undergraduate thesis, using Matlab code I wrote to segment cells and measure their morphology.
\item I tutored math at OSU and SWOCC from 2009 to 2014.
\end{itemize}

\section*{Qualifications}
My qualifications include:
\begin{itemize}
\item six months' experience with the tools and protocols of a cell biophysics lab;
\item an education in POSIX operating systems, AutoCAD, and engineering cost-analysis;
\item a CompTIA A+ PC technician's certification;
\item a passion for innovation and prototyping;
\item a familiarity with \LaTeX, python, C++, xhtml, css, and git; and
\item a fascination with learning new concepts, programming languages, protocols, standards, and best-practices.
\end{itemize}
\end{document}
