 \documentclass[ notitlepage, prl]{ revtex4-1}
%\documentclass[ notitlepage]{ article}
\setlength{\parindent}{0}
\begin{document}
\author{Kyle Thomas}
\title{R\'esum\'e}
\date{\today}
\maketitle
\section*{Objective}
\par I am fulfilled by designing and optimizing innovative products and processes. I am eager to put my creativity to use producing vaue for an employer.
\section*{Education}
\par I received my bachelors of physics from Oregon State University (\textbf {OSU}) in 2015.
\par I received my associates with an emphasis in engineering from Southwestern Oregon Community College (\textbf {SWOCC}) in 2011.
\section*{Work Experience}
\begin{itemize}
\item I proctored exams for various introductory physics courses at OSU during 2014 and 2015. Proctoring was primarily answering students' questions.
\item I wrote my undergraduate thesis about research I undertook in Professor Bo Sun's cell biophysics lab at OSU during 2013 and 2014. 
This research used Matlab code which I wrote to automatically outline user-selected cells in each frame of a movie and measure each cell's size and shape throughout that movie.
\item I tutored math at both OSU and SWOCC from 2009 to 2014.
\end{itemize}

\section*{Qualifications}
My qualifications include:
\begin{itemize}
\item my six months' experience with the tools and protocols of a cell biophysics lab;
\item my education  Linux operating systems, electronics, low-level computer-interfacing, Windows operating systems, and AutoCAD;
\item my CompTIA A+ PC technician's certification;
\item my working knowledge of \LaTeX, python, html, css, and git; and
\item my enjoyment of learning new software, programming languages, and technical standards.
\end{itemize}
\end{document}
